\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://akashkundu.net/}{\Large Akash Kundu}} & Email : \href{mailto:akashkundu92@gmail.com}{akashkundu92@gmail.com}\\
  \href{https://turbulenceintech.com}{TurbulenceInTech.com} & Mobile : (972) 834-8537 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Texas A\&M University}{College Station, TX}
      {B.S. in Computer Science; Minor in Cybersecurity;  \textbf{GPA: 3.3}}{Aug 2015 -- May 2019}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Cisco Systems}{Richardson, TX}
      {Security Solutions Engineering Intern}{May 2018 - Aug 2018}
      \resumeItemListStart
        \resumeItem{Cloud Automation}
          {Developed \& automated AWS job using Python and Jenkins\\ that is now reused frequently for maintenance of AWS environment. Created several\\automation scripts for AWS environment using Boto3.}
        \resumeItem{Serverless}
          {Developed serverless web API that will be used in a company-wide\\  website extension using AWS Lambda, API Gateway and DynamoDB.}
      \resumeItemListEnd

    \resumeSubheading
      {Sympliact}{College Station, TX}
      {iOS Developer Wintern}{December 2017 - Jan 2018}
      \resumeItemListStart
        \resumeItem{iOS Development}
          {Helped integrate Realm Object database into Sympliact iOS\\application.}
      \resumeItemListEnd

    \resumeSubheading
      {Alliance Data Systems}{Plano, TX}
      {Information Security Intern}{Jun 2017 - Aug 2017}
      \resumeItemListStart
        \resumeItem{Automation}
          {Developed PowerShell application that helps analyze security logs\\ that is currently being used by the governance \& compliance team.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {NSCS Member Website}{College Station, TX}
      {Product Manager \& AWS Developer}{Jan 2018 - May 2018}
      \resumeItemListStart
        \resumeItem{Product Manager}
          {Oversaw development of product from conceptualization to\\ delivery. Served as liaison between client and development team.}
          \resumeItem{AWS Developer}
          {Managed IAM for team (during development) and client\\ (upon delivery). Developed website's storage features using AWS S3.}
      \resumeItemListEnd

    \resumeSubheading
      {iOS Apps}{Plano, TX}
      {Sole Developer}{May 2017 - Jan 2018}
      \resumeItemListStart
        \resumeItem{Boba Now}
          {The easiest way to find bubble tea near you.}
        \resumeItem{String Works}
          {Convenient \& swift text alterations.}
        \resumeItem{Fast Phrase}
          {Automate engaging with one's followers via commenting.}
      \resumeItemListEnd

    \resumeSubheading
      {Reading Adventures Web App}{College Station, TX}
      {Full-Stack Developer}{Sept 2018 - December 2018}
      \resumeItemListStart
        \resumeItem{Front-End}
          {Used Angular to deliver responsive and easy user interface\\for web app.}
        \resumeItem{Back-End}
          {Used AWS Dynamo DB, Lambda, and API Gateway to create\\serverless backend that delivered book content to web app.}
      \resumeItemListEnd

    \resumeSubheading
      {TurbulenceInTech.com}{Plano, TX}
      {Sole Developer}{April 2018 - Present}
      \resumeItemListStart
        \resumeItem{Serverless}
          {The website follows the serverless design model using AWS Lambda,\\ S3, and API Gateway.}
        \resumeItem{Blog}
          {The website serves as a resume website as well as a blog that I share my\\ experiences in to help others. Under construction.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
      \textbf{Languages}{: Python, C/C++, PowerShell, Bash, Swift, HTML/JS/TS/CSS, Node.js\\}
      \textbf{Frameworks}{: Angular, Express, Bootstrap\\}
      \textbf{Cloud}{: AWS (Lambda, API Gateway, S3, EC2, IAM) Jenkins, Boto3, Heroku\\}
      \textbf{Database}{: Realm, DynamoDB, MongoDB\\}
      
%-------------------------------------------
\end{document}
